WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-22 article/Article.tex
document strel fuction
darcs-hash:20060322102742-2fc9d-d60350ebc037a3a5616c6dd0654f5aadd8169bb4.gz

  \item \verb$itk.strel$

>>>>

  \item \verb$itk.strel( d, s )$ is used to create a binary ball structuring of dimension
\verb$d$ and size \verb$s$. Strucutring element support is quite bad currently in WrapITK
and should change in the future. Using \verb$itk.strel$ rather than creating a
\verb$BinaryBallStructuringElement$ directly is recommended to have backward compatibility
when the structuring element type will be changed.
